External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising

### 2016-10-13 egpaper_for_review.tex
a

In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are designed to deal with real noisy images. Almost all these methods coincidently employ a two-stage framework: in the first stage, assuming a distribution model (usually Gaussian) on the noise and estimate its parameters; in the second stage, performing denoising with the help of the noise modeling and estimation in the first stage. However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}. Although the mixture of Gaussians (MoG) model is possible to approximate any unknown noise \cite{Zhu_2016_CVPR}, estimating its parameters is often time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR,Bishop}. To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}. This image is captured by a Nikon D800 camera while the ISO is set as 3200. The "ground truth" image is also provided with which we can calculate objective measurements. More details about this dataset can be found at the experimental section. The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image. This proves that the above mentioned methods are not effective on denoising complex noise on real images. 
\begin{figure*}\label{fig1}
\centering
\subfigure{
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) CSF \cite{csf}\\ (35.39dB/0.9677) }
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) MLP \cite{mlp}\\ (34.22dB/0.9603) }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) Mean Image }
\end{minipage}
}
\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

@@

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_5dmark3_iso3200_3_real.png}}
{\footnotesize (a) Noisy Image \\ (33.83dB/0.9128)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_5dmark3_iso3200_3_real.png}}
{\footnotesize (b) Mean Image}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_5dmark3_iso3200_3_real.png}}
{\footnotesize (c) CBM3D \\ (33.84dB/0.9134)   }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_5dmark3_iso3200_3_real.png}}
{\footnotesize (d) CSF \\ (32.62dB/0.9031)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_5dmark3_iso3200_3_real.png}}
{\footnotesize (e) MLP \\ (32.36dB/0.8993)  }
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NC_5dmark3_iso3200_3_real.png}}
{\footnotesize (f) Noise Clinic \\ (35.54dB/0.9476)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NI_5dmark3_iso3200_3_real.png}}
{\footnotesize (g) Neat Image \\ (34.77dB/0.9463)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_WNNM_5dmark3_iso3200_3_real.png}}
{\footnotesize (h) WNNM \\ (33.86dB/0.9143)}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CCNoise_5dmark3_iso3200_3.png}}
{\footnotesize (i) CCNoise \\ (34.91dB/0.9478)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_5dmark3_iso3200_3_real.png}}
{\footnotesize (j) Guided \\ (\textbf{37.01}dB/\textbf{0.9676})}
\end{minipage}
}
\caption{Denoised images of the old image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
\label{fig3}
\end{figure*}

>>>>

In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are designed to deal with real noisy images. Almost all these methods coincidently employ a two-stage framework: in the first stage, assuming a distribution model (usually Gaussian) on the noise and estimate its parameters; in the second stage, performing denoising with the help of the noise modeling and estimation in the first stage. However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}. Although the mixture of Gaussians (MoG) model is possible to approximate any unknown noise \cite{Zhu_2016_CVPR}, estimating its parameters is often time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR,Bishop}. To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}. This image is captured by a Nikon D800 camera while the ISO is set as 3200. The "ground truth" image is also provided with which we can calculate objective measurements. More details about this dataset can be found at the experimental section. The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image. This proves that the above mentioned methods are not effective on denoising complex noise on real images. 
\begin{figure*}\label{fig1}
\centering
\subfigure{
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) MLP \cite{mlp}\\ (34.22dB/0.9603) }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) CSF \cite{csf}\\ (35.39dB/0.9677) }
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) Mean Image }
\end{minipage}
}
\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
\end{figure*}

@@

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_5dmark3_iso3200_3_real.png}}
{\footnotesize (a) Noisy Image \\ (33.83dB/0.9128)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_5dmark3_iso3200_3_real.png}}
{\footnotesize (b) CBM3D \\ (33.84dB/0.9134)   }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_5dmark3_iso3200_3_real.png}}
{\footnotesize (c) MLP \\ (32.36dB/0.8993)  }
\end{minipage}
\centering
\begin{minipage}[t]{0.2\textwidth}
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_5dmark3_iso3200_3_real.png}}
{\footnotesize (d) CSF \\ (32.62dB/0.9031)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_WNNM_5dmark3_iso3200_3_real.png}}
{\footnotesize (e) WNNM \\ (33.86dB/0.9143)}
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NC_5dmark3_iso3200_3_real.png}}
{\footnotesize (f) Noise Clinic \\ (35.54dB/0.9476)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NI_5dmark3_iso3200_3_real.png}}
{\footnotesize (g) Neat Image \\ (34.77dB/0.9463)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CCNoise_5dmark3_iso3200_3.png}}
{\footnotesize (h) CCNoise \\ (34.91dB/0.9478)  }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_5dmark3_iso3200_3_real.png}}
{\footnotesize (i) Guided \\ (\textbf{37.01}dB/\textbf{0.9676})}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_5dmark3_iso3200_3_real.png}}
{\footnotesize (j) Mean Image}
\end{minipage}
}
\caption{Denoised images of the old image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
\label{fig3}
\end{figure*}

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
{\footnotesize (a) Noisy Image   }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
{\footnotesize (b) CBM3D}
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
{\footnotesize (c) MLP }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_dog.png}}
{\footnotesize (d) CSF    }
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
{\footnotesize (e) WNNM    }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
{\footnotesize (f) Noise Clinic   }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
{\footnotesize (g) Neat Image    }
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
{\footnotesize (h) Guided  }
\end{minipage}
}
\caption{Denoised images of the old image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
\label{fig4}
\end{figure*}
